---
title: "Lab 00 - Hello IDS!"
author: "Herman Songe-Aakre"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Herman Songe-Aakre", "Abdulrahman Albinali", "Rudy Adair", 
           "Matthew Hurrel", "Hamish Lothian"),
  github_username = c("hermansokr", "7aman4013", "rudyadair", 
                      "matthurrell", "hamlot12"), 
  colour = c("seagreen4", "blue", "purple2", 
             "red", "steelblue"),
  hobby = c("cricket", "math/coding", "cricket", 
            "badminton", "golf"),
  favourite_number = c(sample(10, size = 1), 2, 5, 6, 9)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows the favourite number given the username of each user, the columns of the usernames in their favourite colour. 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username on Github", 
          y = "Favourite number",
          title = "Favourite numbers of the team")
```

Labs changes the labels of a plot.
### Exercise 20
LETTERS=[A,B,C,D,E,F,G]
```{r new-bar-plot}

p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar(fill = paste0(sample(c(0:9, LETTERS[0:6]), 6, T)) )
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
